\documentclass[12pt]{article}

\usepackage[a4paper, margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\title{\textbf{Impact-Driven Productivity System:\\
Mapping Digital Focus to Real-World Social Impact}}

\author{Hariom Mewada \\
Department of Computer Science \\
Indian Institute of Technology}

\date{\today}

\begin{document}

\maketitle

\section{Introduction}

Digital productivity applications use gamification to improve user focus and engagement. 
However, most systems provide symbolic rewards (e.g., virtual points, trees, badges) 
without measurable real-world outcomes.

This project proposes an Impact-Driven Productivity System that connects user focus 
sessions to quantifiable real-world social impact such as water purification, 
pollution reduction, and education support.

\section{Problem Statement}

Existing focus applications provide virtual rewards but lack:
\begin{itemize}
    \item Transparent real-world impact mapping
    \item Measurable social contribution metrics
    \item Behavioral reinforcement grounded in meaningful outcomes
\end{itemize}

The central research question is:

\textit{Can mapping productivity sessions to measurable real-world social impact 
increase sustained user engagement compared to symbolic gamification systems?}

\section{Proposed System Architecture}

The system will consist of:

\begin{enumerate}
    \item \textbf{Focus Tracking Module} – Tracks Pomodoro sessions and deep work intervals.
    \item \textbf{Impact Conversion Engine} – Converts completed sessions into measurable social impact units.
    \item \textbf{Impact Dashboard} – Displays cumulative personal and community impact metrics.
    \item \textbf{Backend Infrastructure} – Maintains secure logging and transparent impact records.
\end{enumerate}

\section{Technical Contributions}

\begin{itemize}
    \item A scalable architecture for mapping digital actions to real-world impact metrics.
    \item Transparent accounting model for impact verification.
    \item Behavioral engagement evaluation framework.
    \item Modular integration framework for NGO or CSR partnerships.
\end{itemize}

\section{Evaluation Methodology}

We propose a controlled study:

\begin{itemize}
    \item Group A: Standard gamified focus application.
    \item Group B: Impact-driven focus application.
\end{itemize}

Metrics to evaluate:
\begin{itemize}
    \item Session completion rate
    \item Retention rate
    \item Average weekly usage time
    \item Long-term engagement
\end{itemize}

\section{Expected Outcomes}

\begin{itemize}
    \item Increased motivation through meaningful rewards.
    \item Improved long-term engagement compared to symbolic gamification.
    \item Deployable prototype system.
\end{itemize}

\section{Conclusion}

This project bridges productivity systems and measurable social impact. 
By combining behavioral modeling, gamification, and transparent impact tracking, 
the system aims to transform digital focus into tangible societal benefit.

\end{document}